Synthesising and Verifying Closed-loop Digital Control Systems

### 2016-09-21 paper/paper.tex
general description of the synthesiser

\paragraph{General architecture of the program synthesiser}
%
The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}.

\paragraph{Elements specific to control systems}

>>>>

\paragraph{General architecture of the program synthesiser}
%
The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs}.
The {\sc synth} procedure tries to find an existential witness $P$
that satisfies the specification $\sigma(x, P)$ for all $x$:
%
$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$

If {\sc synthesise} succeeds in finding a witness $P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to {\sc verify} which determines whether it does satisfy
the specification on all inputs by checking satisfiability of the
verification formula:
%
$\exists x . \lnot \sigma(x, P)$

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates. 
Otherwise, the witness $x$ is an input on which the candidate solution fails
to meet the specification.  This witness $x$ is added to the {\sc inputs}
set and the loop iterates again.  It is worth noting that each iteration of the
loop adds a new input to the set of inputs being used for synthesis.  If
the full set of inputs is finite, this means that the refinement loop
can only iterate a finite number of times.

\paragraph{Elements specific to control systems}
\cdsay{discussion on the noise introduced by the plant modelling?}
